Meta-analysis

### 2019-11-12 03_Preliminary_analysis.Rmd
tiny changes to spelling, load libraries, etc

```{r PA_Libraries, include=FALSE}
library(tidyverse)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(devtools)
library(lme4)
library(theme.usq)
source("R/import_data.R")
#source("./getPPD2.R")
```

@@

   9) irrigated vs non-irrigated trials

@@

   12) Two pathogen species cause PM (new discovery)

>>>>

```{r PA_Libraries, include=FALSE}
library(tidyverse)
library(bomrang)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(devtools)
library(lme4)
library(theme.usq)
source("R/import_data.R")
#source("./getPPD2.R")
```

@@

   9) Irrigated vs non-irrigated trials

@@

   12) Two pathogen species cause PM (new discovery in 2018)
